Beyoncé

### 2024-04-15 paper/paper.qmd
Add figure to results section

beyonce_cleaned |>
  ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
  geom_point() +
  theme_minimal() +
  labs(x = "Weeks on Chart", y = "Spotify Streams", color = "Album")
```

@@

>>>>

beyonce_cleaned |>
  ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
  geom_point(alpha = 0.5) +
  theme_minimal() +
  labs(x = "Weeks on Chart", y = "Spotify Streams", color = "Album")
```

@@

```{r}
#| echo: false
#| label: fig-prediction
#| fig-cap: "The predicted number of Spotify streams for a Beyoncé song based on the number of weeks spent on the *Billboard Hot 100*"

plot_predictions(beyonce_nbinom, condition = "wks_on_chart") +
  labs(x = "Weeks on Chart",
       y = "Spotify Streams") +
  theme_classic()
```
